\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
I acknowledge the traditional owners of the land upon which I was afforded the opportunity to complete this thesis, the Ngunnawal people. I acknowledge that this land was never ceded and and thank elders, both past and present, of the Ngunnawal people, and other first nations groups across the country.\par
Thank you to my supervisors, Ramesh and Mike, without both of your help throughout this thesis would never have gotten off the ground - much less been completed. Specifically, I want to thank Ramesh, for what has been going on three years now (wow - time flies), of guidance and advice. I also want to thank Mike, for always reminding me of the need to address the pending criticism from the person in the back of the room with their hand up - well before they have the chance to ask their question!\par
Thank you to Matthew Hole and Ashley Barnes for your assistance in helping me break though into the jargon filled world of network tomography and giving me a starting code repository, without which I would have been lost. I also want to thank Matthew for allowing me to piggy back on his Gadi project, even after receiving email warnings from NCI staff about my overly-ambitious CPU allocation requests.\par
Thank you to my gorgeous Mum, for all the phone calls checking in, always being willing to endure my whingeing about whatever had annoyed me that week, and helping me get to were I am today. Thank you to my amazing grandparents, for all your love and always believing in me. I also would be remissed if I didn't thank Garg, for taking the time to proof read this thesis, and for always being an example of organisation and perseverance to aspire to.\par
Thank you to Cole and Peter, for a great year at Scrivener street and always being around to help me switch off (sometimes perhaps a little too frequently) with an episode of Lost or some RawFM. Thank you to all my friends, from Brisbane and Canberra alike, for always being there for me (special shout-out to Ashan and El Grande Hird). And thank you to my cat Flip, for being a constant source of both comfort and irritation.\par
Last but far from least, thank you to my amazing girlfriend Olivia, for all your love and support throughout this year, all those previous, and all those to come. Without you I would have given up a long time ago. 